Figures to insert in text

### 2018-03-16 Chapters/sdm-validation.tex
SDM more grammar and typo fixes

In figure \ref{fig:validation-distance}, we can notice that the theoretical model and the simulation matches. Hence, it seems the random bitstring generation algorithm works properly.

@@

In figure \ref{fig:validation-activated-hls}, we can notice that the theoretical model and the simulation matches. Hence, it seems that both the address space generation algorithm and the scan algorithm work properly. Notice that the curve is almost the same for $n=1,000$ and $n=256$. It happens because the access radius is adjusted to get $p$ as close as possible to $0.001$. They are not exactly the same because their $p$ differs a little.

@@

Kanerva has calculated the intersection of two circles according to the distance between their centers. The intersection is important to understand how SDM works because it affects directly the critical distance. When $\eta_d$ is inside the critical distance, then it will converge to $\eta$. In fact, it converges because they share a sufficient amount of hard locations, i.e., the intersection of the circle around $\eta_d$ and $\eta$ is enough to converge. For further information about the relation between the critical distance and the intersection, see \citet{brogliato2014sparse}.

@@

We have tested exactly the same example presented in \citet{Kanerva1988}, p.85. We wrote two sequences to a $3$-fold memory: $<A, B, C, D>$ and $<E, B, C, F>$. Then, after reading the sequences $<A, B, C>$ and $<E, B, C>$, we have obtained $D$ and $F$, respectively.

@@

The logic behind how it works is that, when reading the sequence $<A, B, C>$, we have $A$ pointing to $D$, while both $B$ and $C$ point to $D$ and $F$. Thus, $D$ appears more often than $F$ and ended up being the result.

Hence, as we have replicated the theoretical results from Kanerva, we have one more evidence that our framework works properly.

>>>>

In figure \ref{fig:validation-distance}, we can notice that the theoretical model and the simulation matches. Hence, it seems the random bitstring generation algorithm works appropriately.

@@

In figure \ref{fig:validation-activated-hls}, we can notice that the theoretical model and the simulation matches. Hence, it seems that both the address space generation algorithm and the scan algorithm work properly. Notice that the curve is almost the same for $n=1,000$ and $n=256$. This difference happens because the access radius is adjusted to get $p$ as close as possible to $0.001$, which mean they are very close, but not the same.

@@

Kanerva has calculated the intersection of two circles according to the distance between their centers. The intersection is important to understand how SDM works because it directly affects the critical distance. When $\eta_d$ is inside the critical distance, then it will converge to $\eta$. In fact, it converges because they share a sufficient amount of hard locations, i.e., the intersection of the circle around $\eta_d$ and $\eta$ is enough to converge. For further information about the relation between the critical distance and the intersection, see \citet{brogliato2014sparse}.

@@

We have tested the same example presented in \citet{Kanerva1988}, p.85. We wrote two sequences to a $3$-fold memory: $<A, B, C, D>$ and $<E, B, C, F>$. Then, after reading the sequences $<A, B, C>$ and $<E, B, C>$, we have obtained $D$ and $F$, respectively.

@@

The logic behind how it works is that, when reading the sequence $<A, B, C>$, we have $A$ pointing to $D$, while both $B$ and $C$ point to $D$ and $F$. Thus, $D$ appeared more often than $F$ and ended up being the result.

Hence, as we have replicated the theoretical results from Kanerva, we have one more evidence that our framework works appropriately.

### 2018-03-16 Chapters/sdm2.tex
SDM more grammar and typo fixes

In traditional memory, each datum is stored in an address and every look up of a specific datum requires a search through the memory. In spite of computer scientists having developed beautiful algorithms to perform fast searches, almost all of them do a precise search. That is, if you have an imprecise clue of what you need, these algorithms will simply fail.

@@

When reading a cue $\eta_{x}$ that is $x$ bits away from $\eta$, the cue shares many addresses with $\eta$. The number of shared addresses decreases as the cue's distance to $\eta$ increases, in other words, as $x$ increases. This is shown in Figure \ref{fig-shared-addresses}.  The target datum $\eta$ was written in all shared addresses, thus they will bias the read output in the direction of $\eta$. If the cue is sufficiently near the target datum $\eta$, the read output will be closer to $\eta$ than $\eta_{x}$ was. Repeating the read operation increasingly gets results closer to $\eta$, until it is exactly the same. So, it may be necessary to perform more than one read operation in order to converge to the target data $\eta$.

@@

The addresses of the $\{0,1\}^{n}$ space grow exponentially with the number of dimensions $n$, i.e. $N=2^{n}$. For $n=100$ we have $N\approx10^{30}$, which is incredibly large when related to a computer memory. Furthermore, \citet{Kanerva1988} suggests $n$ between 100 and 10,000. Recently he has postulated 10,000 as a desirable minimum $N$ (personal communication). To solve the feasibility problem of implementing this memory, Kanerva made a random sample of $\{0,1\}^{n}$, in his work, having $N'$ elements. All these addresses in the sample are called hard locations. Other elements of $\{0,1\}^{n}$, not in $N'$, are called virtual neurons. This is represented in Figure \ref{fig-hardlocations}.  All properties of reading and write operations presented before remain valid, but limited to hard locations. Kanerva suggests taking a sample of about one million hard locations.

@@

Since a cue $\eta_{x}$ near the target bitstring $\eta$ shares many hard locations with $\eta$, SDM can retrieve data from imprecise cues. Despite this feature, it is very important to know how imprecise this cue could be while still giving accurate results. What is the maximum distance from our cue to the original data that still retrieves the right answer? An interesting approach is to perform a read operation with a cue $\eta_{x}$, that is $x$ bits away from the target $\eta$.  Then measure the distance from the read output and $\eta$. If this distance is smaller than $x$ we are converging. Convergence is simple to handle, just read again and again, until it converges to the target $\eta$. If this distance is greater than $x$ we are diverging. Finally, if this distance equals $x$ we are in a tip-of-the-tongue process.  A tip-of-the-tongue psychologically happens when you know that you know, but you can't say what exactly it is. In SDM mathematical model, a tip-of-the-tongue process takes infinite time to converge. \citet{Kanerva1988} called this $x$ distance, where the read's output averages $x$, the critical distance. Intuitively, it is the distance from which smaller distances converge and greater distances diverge. In Figure \ref{fig-p1-p2-iterative-read}, the circle has radius equal to the critical distance and every $\eta_{x}$ inside the circle should converge.  The figure also shows a convergence in four readings.

@@

A random bitstring is generated with equal probability of $0$'s and $1$'s in each bit. One can readily see that the average distance between two random bitstrings has binomial distribution with mean $n/2$ and standard deviation $\sqrt{n/4}$. For a large $n$, most of the space lies close to the mean and has fewer shared hard locations.  As two bitstrings with distance far from $n/2$ are very improbable, \citet{Kanerva1988} defined that two bitstrings are orthogonal when their distance is $n/2$.

@@

This mapping from concepts to bitstrings brings us two main questions: (i) Suppose we have a bitstring that is linking two major concepts.  How do we know which concepts are linked together? (ii) From a concept bitstring, how can we list all concepts that are somehow linked to it? This second question is called the problem of spreading activation.

>>>>

In traditional memory, each datum is stored in an address and every lookup of a specific datum requires a search through the memory. In spite of computer scientists having developed beautiful algorithms to perform fast searches, almost all of them do a precise search. That is, if you have an imprecise clue of what you need, these algorithms will simply fail.

@@

When reading a cue $\eta_{x}$ that is $x$ bits away from $\eta$, the cue shares many addresses with $\eta$. The number of shared addresses decreases as the cue's distance to $\eta$ increases, in other words, as $x$ increases. This is shown in Figure \ref{fig-shared-addresses}.  The target datum $\eta$ was written in all shared addresses, thus they will bias the read output in the direction of $\eta$. If the cue is sufficiently near the target datum $\eta$, the read output will be closer to $\eta$ than $\eta_{x}$ was. Repeating the read operation increasingly gets results closer to $\eta$, until it is precisely the same. So, it may be necessary to perform more than one read operation to converge to the target data $\eta$.

@@

The addresses of the $\{0,1\}^{n}$ space grow exponentially with the number of dimensions $n$, i.e., $N=2^{n}$. For $n=100$ we have $N\approx10^{30}$, which is incredibly large when related to computer memory. Furthermore, \citet{Kanerva1988} suggests $n$ between 100 and 10,000. Recently he has postulated 10,000 as a desirable minimum $N$ (personal communication). To solve the feasibility problem of implementing this memory, Kanerva made a random sample of $\{0,1\}^{n}$, in his work, having $N'$ elements. All these addresses in the sample are called hard locations. Other elements of $\{0,1\}^{n}$, not in $N'$, are called virtual neurons. This is represented in Figure \ref{fig-hardlocations}.  All properties of reading and write operations presented before remain valid but limited to hard locations. Kanerva suggests taking a sample of about one million hard locations.

@@

Since a cue $\eta_{x}$ near the target bitstring $\eta$ shares many hard locations with $\eta$, SDM can retrieve data from imprecise cues. Despite this feature, it is very important to know how imprecise this cue could be while still giving accurate results. What is the maximum distance from our cue to the original data that still retrieves the right answer? An interesting approach is to perform a read operation with a cue $\eta_{x}$, that is $x$ bits away from the target $\eta$.  Then measure the distance from the read output and $\eta$. If this distance is smaller than $x$ we are converging. Convergence is simple to handle, just read again and again, until it converges to the target $\eta$. If this distance is greater than $x$ we are diverging. Finally, if this distance equals $x$ we are in a tip-of-the-tongue process.  A tip-of-the-tongue psychologically happens when you know that you know, but you can't say what exactly it is. In SDM mathematical model, a tip-of-the-tongue process takes infinite time to converge. \citet{Kanerva1988} called this $x$ distance, where the read's output averages $x$, the critical distance. Intuitively, it is the distance from which smaller distances converge and greater distances diverge. In Figure \ref{fig-p1-p2-iterative-read}, the circle has radius equal to the critical distance and every $\eta_{x}$ inside the circle should converge.  The figure also shows convergence in four readings.

@@

A random bitstring is generated with equal probability of $0$'s and $1$'s in each bit. One can readily see that the average distance between two random bitstrings follows the binomial distribution with mean $n/2$ and standard deviation $\sqrt{n/4}$. For a large $n$, most of the space lies close to the mean and has fewer shared hard locations.  As two bitstrings with distance far from $n/2$ are very improbable, \citet{Kanerva1988} defined that two bitstrings are orthogonal when their distance is $n/2$.

@@

This mapping from concepts to bitstrings brings us two central questions: (i) Suppose we have a bitstring that is linking two major concepts.  How do we know which concepts are linked together? (ii) From a concept bitstring, how can we list all concepts that are somehow linked to it? This second question is called the problem of spreading activation.
